Corner Localization and Camera Calibration from Imaged Lattices

### 2023-08-14 paper/presentation.tex
Update the notation

\documentclass{beamer}
% \documentclass[notes]{beamer}

@@

\usepackage{graphicx}
% \usepackage{booktabs}
% \usepackage{algorithm}
% \usepackage{algpseudocode}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{pgf-pie}
% \usepackage{tikz}
% \usepackage{upgreek}
\usepackage{appendixnumberbeamer}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{pgfplots}
% \usepackage{url}
\usepackage{xfrac}
\usepackage{appendixnumberbeamer}

% \usetikzlibrary{calc}
% \usetikzlibrary{3d}
\usetikzlibrary{spy,arrows}

@@

@@

\begin{frame}
	\titlegraphic{\hfill\includegraphics[height=1cm]{UCU-Apps2022_.png}}
	\titlepage
\end{frame}

\begin{frame}
	\frametitle{Structure of the presentation}
	\tableofcontents
\end{frame}

@@

\begin{frame}
	\frametitle{Motivation}
	Accurate camera calibration is required for many applications, such as:
	\begin{itemize}
		\item 3D reconstruction
		\item Robotics and automation
		\item Augmented reality
		\item Photogrammetry
		\item Stereo vision
		\item And many more\ldots
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Challenges}
	% \begin{columns}[T,onlytextwidth]
	% \column{0.6\textwidth}
	Camera calibration is
	a challenging task, especially for highly distorted images.

	The challenges include:
	\begin{itemize}
		\item Robust keypoint detection
		\item Accurate distortion modeling
		\item Stability of the calibration
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Example}
	% \column{0.4\textwidth}
	\begin{figure}
		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=3cm, connect spies}]
			\node[anchor=south west,inner sep=0] (image) at (0,0)
			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
			{\includegraphics[width=0.8\textwidth]{distorted_image}};
			\begin{scope}[x={(image.south east)},y={(image.north west)}]
				\spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
				\spy[blue] on (3.5,3.0) in node [right] at (8.1,4.3);
			\end{scope}
		\end{tikzpicture}
		\caption{Example of corners near the center of the image and at the edge}
	\end{figure}
	% \end{columns}
\end{frame}

\begin{frame}
	\frametitle{Research objective}

	Improve the detection of
	calibration board fiducials from calibration imagery taken by wide-angle or
	fisheye lenses.

@@

\section{Background}\label{sec:background}

\begin{frame}
	\frametitle{Notation}
	The column vectors will be denoted by bold lowercase letters (e.g.
	\(\mathbf{u} = \begin{pmatrix}
		u, v, 1
	\end{pmatrix}^{T}\)), matrices will be denoted by bold uppercase letters (e.g.
	\(H = \begin{bmatrix}
		\mathbf{r_1} & \mathbf{r_2} & \mathbf{t}
	\end{bmatrix}
	\)). We will use homogeneous coordinates to simplify the equations.
\end{frame}

@@

\begin{frame}
	\frametitle{Definition of the camera model}
	\begin{exampleblock}{Definition}
		\begin{align}
			\alpha \mathbf{u} & = K f_{\boldsymbol{\lambda}}(H\mathbf{X})
			\tag{Projection} \label{eq:projection}                                            \\
			\alpha \mathbf{X} & = H^{-1} g_{\boldsymbol{\lambda}}(K^{-1}\mathbf{u}) \tag{Back
				projection} \label{eq:back_projection}.
		\end{align}
		where \(K\) is the camera matrix, \(g_{\boldsymbol{\lambda}}(\cdot)\) is the division distortion
		model \citep{fitzgibbonSimultaneousLinearEstimation2001}, \(f(\cdot)\) is the
		inverse of \(g(\cdot)\) and \(H\) is the homography matrix, and \(\alpha\)
		is a non-zero scalar.
	\end{exampleblock}

	\begin{alertblock}{Note}
		Slides with the detailed explanation can be demonstrated upon request during the Q\&A session.
		% The explanation of the used camera model does not fit into the
		% presentation duration. However, the appendix of this presentation contains
		% the detailed explanation of each element of the equation, and will be
		% happily discussed/presented during the Q\&A session.
	\end{alertblock}

@@

	\begin{enumerate}
		\item Feature detection.
		\item Camera calibration.
		      \begin{enumerate}
			      \item Initialize camera parameters (\(R\), \(\mathbf{t}\),
			            \(\boldsymbol{\lambda}\)) using the solver.
			      \item Refine camera parameters and estimate \(K\) by optimization.
		      \end{enumerate}
		\item Impute the gaps in the board, and extend it.
		\item Get positions of new points on the image.
		\item Filter out false positives.
	\end{enumerate}
\end{frame}

@@

	\begin{enumerate}
		\item Initialize camera parameters (\(R\), \(\mathbf{t}\),
		      \(\boldsymbol{\lambda}\)) using the method, proposed by
		      \cite{scaramuzzaToolboxEasilyCalibrating2006}.
	\end{enumerate}
	\begin{exampleblock}{Overview}
		The author proposes the multistage solver for the projection equation,
		assuming that the camera matrix is known.
	\end{exampleblock}
\end{frame}

\begin{frame}
	\frametitle{Camera calibration 2}
	\begin{enumerate}
		\item Refine the values of \(R\), \(\mathbf{t}\), \(\boldsymbol{\lambda}\), and
		      estimate \(K\) by minimizing the reprojection error between the
		      board and the back-projected corners.
	\end{enumerate}

@@

\begin{frame}
	\frametitle{Binary classification}
	\begin{itemize}
		\item Compute the corner likelihood map for the image.
		\item Use the ROC curve, and pick the threshold which maximizes the G-mean.
	\end{itemize}

@@

\begin{frame}
	\frametitle{Camera calibration 1}
	Compare the initial camera calibration with camera calibration obtained via
	optimization of reprojection error.

@@

	The Hessian approach proved to be more robust, as the other gave too many false
	positives, especially for the edges.

@@

\begin{frame}
	\frametitle{Evaluation (artificially removed points)}
	We removed 20\% of the points from the original board and then tried to recover
	them.

@@

\end{frame}
\begin{frame}
	\frametitle{Evaluation (artificially removed points) 2}
	\begin{figure}
		\centering
		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
		\caption{Recovered pruned points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
		\caption{Feature refinement on the board with 80\% of the points}
	\end{figure}

@@

	Occlusions pose additional complications for feature detection.

@@

\end{frame}
\begin{frame}
	\frametitle{Evaluation (artificial occlusion) 2}
	\begin{figure}
		\begin{subfigure}[h]{\linewidth}
			\centering
			\includegraphics[width=0.7\linewidth]{refined_overlayed_corners.png}
			\caption{Recovered pruned points
				(\textcolor[HTML]{1f77b4}{unchanged}
				\textcolor[HTML]{ff7f0e}{filtered out}
				\textcolor[HTML]{2ca02c}{new corner}
				\textcolor[HTML]{d62728}{out of image})}
		\end{subfigure}
		\hfill
		\caption{Feature refinement on the board with partial board occlusion}
	\end{figure}

@@

	% \begin{minipage}[t]{0.80\linewidth}
	\begin{figure}[h]
		\centering
		\includegraphics[width=0.75\linewidth]{refined_corners1.png}
		\includegraphics[width=0.75\linewidth]{refined_corners2.png}

		\caption{Recovered points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
		\label{fig:recovered_good_points}
	\end{figure}
	% \end{minipage}

@@

\begin{frame}
	\frametitle{Evaluation (real data, false positives) 1}

	\begin{figure}
		\includegraphics[width=0.8\linewidth]{refined_corners_bad.png}
		\caption{Occlusion on the board with distinct features}
	\end{figure}

\begin{frame}
	\frametitle{Evaluation (real data, false positives) 2}
	\begin{figure}
		\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
		% \caption{Similar pattern to the board in the background}
	\end{figure}

@@

@@

\begin{frame}
	\frametitle{Reviewers' comments}

	\textbf{No comparison was made to classical camera calibration results and no
		discussion why results differ.}

	The main contribution is the feature detection step. The user can use the
	found camera parameters, or pass the obtained features to any camera
	calibration toolchain.
\end{frame}

>>>>

% \documentclass[aspectratio=169]{beamer}
\documentclass{beamer}
% \documentclass[notes]{beamer}

@@

\usepackage{graphicx}
% \usepackage{booktabs}
% \usepackage{algorithm}
% \usepackage{algpseudocode}
\usepackage{subcaption}
\usepackage{pifont}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{caption}
\usepackage{pgf-pie}
% \usepackage{tikz}
% \usepackage{upgreek}
\usepackage{appendixnumberbeamer}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{pgfplots}
% \usepackage{url}
\usepackage{xfrac}
\usepackage{appendixnumberbeamer}

% \usetikzlibrary{calc}
% \usetikzlibrary{3d}
\usetikzlibrary{spy,arrows,shapes, arrows, positioning}

@@

\newcolumntype{L}{>{\raggedright\arraybackslash}X}

\newcommand\headercell[1]{%
   \smash[b]{\begin{tabular}[t]{@{}c@{}} #1 \end{tabular}}}

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

@@

\begin{frame}[plain]
	\titlegraphic{\hfill\includegraphics[height=1cm]{UCU-Apps2022_.png}}
	\titlepage
\end{frame}

% \begin{frame}
% 	\frametitle{Structure of the presentation}
% 	\tableofcontents
% \end{frame}

@@

% \begin{frame}
% 	\frametitle{Motivation}
% 	Accurate camera calibration is required for many applications, such as:
% 	\begin{itemize}
% 		\item 3D reconstruction
% 		\item Robotics and automation
% 		\item Augmented reality
% 		\item Photogrammetry
% 		\item Stereo vision
% 	\end{itemize}
% \end{frame}

\begin{frame}
	\frametitle{Motivation}

	\begin{columns}[T,onlytextwidth]
		\column{0.6\textwidth}
		Accurate camera calibration is required for many applications, such as:
		\begin{itemize}
			\item 3D reconstruction
			\item Robotics and automation
			\item Augmented reality
			\item Photogrammetry
			\item Stereo vision
		\end{itemize}

		\column{0.4\textwidth}
		\begin{figure}
			\centering
			\includegraphics[width=0.8\textwidth]{high_distortion.png}
			\caption{Image with a high distortion}
		\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Example}
	% \column{0.4\textwidth}
	\begin{figure}
		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=3cm, connect spies}]
			\node[anchor=south west,inner sep=0] (image) at (0,0)
			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
			{\includegraphics[width=0.8\textwidth]{distorted_image}};
			\begin{scope}[x={(image.south east)},y={(image.north west)}]
				\spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
				\spy[blue] on (3.5,3.0) in node [right] at (8.1,4.3);
			\end{scope}
		\end{tikzpicture}
		\caption{Corners near the center of the image and at the edge}
	\end{figure}
	% \end{columns}
\end{frame}

\begin{frame}
	\frametitle{Research objective}
	\textbf{Improve the detection of
		calibration board fiducials from calibration imagery taken by wide-angle or
		fisheye lenses.}

@@

\section{Related work}\label{sec:related_work}

\begin{frame}
	\frametitle{TartanCalib\footcite{duisterhofTartanCalibIterativeWideAngle2022}}

	\begin{columns}
		\begin{column}{0.4\textwidth}
			\textbf{Algorithm}
			\begin{enumerate}
				\item Run the calibration toolchain
				\item Undistort the image
				\item Subpixel refinement
				\item Repeat
			\end{enumerate}
		\end{column}
		\begin{column}{0.6\textwidth}
			\textbf{Issues}
			\begin{itemize}
				\item Runs complete calibration toolchain each iteration
				\item Does not use the geometry information
				\item Not self-contained
			\end{itemize}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Models comparison}
	\begingroup
	\scriptsize

	% \begin{figure}
	% 	\begin{subfigure}{0.45\linewidth}
	% 		\resizebox{\linewidth}{!}{
	% 			\centering
	% 			\begin{tikzpicture}
	% 				\begin{axis}[
	% 						xlabel={$x$},
	% 						ylabel={$y$},
	% 						grid=major,
	% 						title={Original board},
	% 					]
	% 					\addplot[
	% 						only marks,
	% 					] table {data/original_board.txt};
	% 				\end{axis}
	% 			\end{tikzpicture}
	% 		}
	\setlength\tabcolsep{1.5pt} % default value: 6pt
	\begin{table}
		\begin{tabularx}{\textwidth}{@{} L *{5}{c} @{}}
			\toprule
			\multicolumn{1}{c}{\multirow{2}{*}{\centering\textbf{Supports}}}           &
			\multicolumn{5}{c@{}}{\textbf{Name}}                                                           \\
			\cmidrule(l){2-6}                                                          &
			\textbf{OpenCV\footcite{dudaAccurateDetectionLocalization2018}}            &
			\textbf{TartanKalib\footcite{duisterhofTartanCalibIterativeWideAngle2022}} &
			\textbf{Kalibr\footcite{mayeSelfsupervisedCalibrationRobotic2013}}         &
			\textbf{OCamCalib\footcite{scaramuzzaToolboxEasilyCalibrating2006}}        &
			\textbf{LIBCBDETECT\footcite{geigerAutomaticCameraRange2012}}                                  \\
			\midrule
			Unknown board shape                                                        & \xmark & \cmark &
			\cmark                                                                     & \cmark & \cmark   \\
			\hline
			Occlusion                                                                  & \xmark & \cmark &
			\cmark                                                                     & \cmark & \cmark   \\
			\hline
			Model-based extra features detection                                       & \xmark & \cmark &
			\xmark                                                                     & \xmark & \xmark   \\
			\hline
			Geometry-based extra features detection                                    & \xmark & \xmark &
			\xmark                                                                     & \xmark & \xmark   \\
			\bottomrule
		\end{tabularx}
		\caption{Comparison of feature detectors}
	\end{table}
	\endgroup
\end{frame}

% \section*{Intuition}\label{sec:intuition}
%
\begin{frame}
	\frametitle{Intuition (image)}
	Can you guess where the missing corners could be?

	% \begin{figure}
	% 	\includegraphics[width=0.7\textwidth]{example_board.png}
	% 	\caption{Example board detection}
	% \end{figure}
	\begin{figure}
		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=3,size=5cm, connect spies}]
			\node[anchor=south west,inner sep=0] (image) at (0,0)
			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
			{\includegraphics[width=0.7\linewidth]{example_board.png}};
			\begin{scope}[x={(image.south east)},y={(image.north west)}]
				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
				\spy[blue] on (5.5,1.0) in node [right] at (6.5,3.3);
			\end{scope}
		\end{tikzpicture}
		\caption{Example board detection}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Intuition (corners)}
	Can you now?

	\begin{figure}
		\resizebox{0.7\textwidth}{!}{
			\centering
			\begin{tikzpicture}
				\begin{axis}[
						xlabel={$x$},
						ylabel={$y$},
						grid=major,
						title={Corners},
					]
					\addplot[
						only marks,
					] table {data/example_corners.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Intuition (board)}
	What about here?

	\begin{figure}
		\resizebox{0.7\textwidth}{!}{
			\centering
			\begin{tikzpicture}
				\begin{axis}[
						xlabel={$x$},
						ylabel={$y$},
						grid=major,
						title={Board},
					]
					\addplot[
						only marks,
					] table {data/example_board.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{figure}
\end{frame}

\begin{frame}[standout]
	Use the board's geometry to find missing corners!
\end{frame}

\section*{Method}\label{sec:method}

	\begin{enumerate}
		\item Feature detection.
		\item Camera calibration.
		      \begin{enumerate}
			      \item Initialize camera parameters using the solver.
			      \item Refine camera parameters by optimization.
		      \end{enumerate}
		\item Impute the gaps in the board and extend it.
		\item Get positions of new points on the image.
		\item Filter out false positives.
	\end{enumerate}
\end{frame}

\begin{frame}
	\frametitle{Notation}
	The column vectors will be denoted by bold lowercase letters (e.g.
	\(\mathbf{u} = \begin{pmatrix}
		u, v, 1
	\end{pmatrix}^{T}\)), matrices will be denoted by uppercase letters (e.g.
	\(H = \begin{bmatrix}
		\mathbf{r_1} & \mathbf{r_2} & \mathbf{t}
	\end{bmatrix}
	\)). We will use homogeneous coordinates to simplify the equations.
\end{frame}

@@

\begin{frame}
	\frametitle{Definition of the camera model}
	\begin{exampleblock}{Definition}
		\begin{align}
			\alpha \mathbf{u} & = K f_{\boldsymbol{\lambda}}(H\mathbf{x})
			\tag{Projection} \label{eq:projection}                                            \\
			\beta \mathbf{x}  & = H^{-1} g_{\boldsymbol{\lambda}}(K^{-1}\mathbf{u}) \tag{Back
				projection} \label{eq:back_projection}.
		\end{align}
		where \(K\) is the camera matrix, \(g_{\boldsymbol{\lambda}}(\cdot)\) is the division distortion
		model \footcite{fitzgibbonSimultaneousLinearEstimation2001}, \(f(\cdot)\) is the
		inverse of \(g(\cdot)\) and \(H\) is the homography matrix, and \(\alpha,
		\beta\) are non-zero scalars.
	\end{exampleblock}

	\begin{alertblock}{Note}
		You have printed materials with the details about the camera model.
		% Slides with the detailed explanation can be demonstrated upon request during the Q\&A session.
		% The explanation of the used camera model does not fit into the
		% presentation duration. However, the appendix of this presentation contains
		% the detailed explanation of each element of the equation, and will be
		% happily discussed/presented during the Q\&A session.
	\end{alertblock}

@@

@@

	Initialize camera parameters (\(R\), \(\mathbf{t}\),
	\(\boldsymbol{\lambda}\)) using the method, proposed by
	\cite{scaramuzzaToolboxEasilyCalibrating2006}.

	\begin{exampleblock}{Overview}
		The author proposes the multistage solver for the projection equation,
		assuming that the camera matrix is known.
	\end{exampleblock}
\end{frame}

	Refine the values of \(R\), \(\mathbf{t}\), \(\boldsymbol{\lambda}\), and
	estimate \(K\) by minimizing the reprojection error between the
	board and the back-projected corners.

@@

\begin{frame}
	\frametitle{Binary classification}
	\begin{itemize}
		\item Compute the corner likelihood map for the image.
		\item Use the ROC curve and pick the threshold which maximizes the G-mean.
	\end{itemize}

@@

\begin{frame}
	\frametitle{Camera calibration 1}
	Compare the initial camera calibration with the camera calibration obtained via
	optimization of reprojection error.

@@

	The Hessian approach proved to be more robust, as the alternative gave too many false
	positives, especially for the edges.

@@

\begin{frame}
	\frametitle{Evaluation (artificially removed points)}
	We removed 20\% of the points and then tried to recover them.

@@

\end{frame}
\begin{frame}
	\frametitle{Evaluation (artificially removed points) 2}

	\begin{figure}
		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=3,size=4cm, connect spies}]
			\node[anchor=south west,inner sep=0] (image) at (0,0)
			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
			{\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}};
			\begin{scope}[x={(image.south east)},y={(image.north west)}]
				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
				\spy[blue] on (3.5,3.0) in node [right] at (6.1,3.3);
			\end{scope}
		\end{tikzpicture}
		\caption{Feature recovery on the board with 80\% of the points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{figure}

@@

	Occlusions pose complications for feature detection.

@@

\end{frame}
\begin{frame}
	\frametitle{Evaluation (artificial occlusion) 2}

	\begin{figure}
		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=3,size=5cm, connect spies}]
			\node[anchor=south west,inner sep=0] (image) at (0,0)
			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
			{\includegraphics[width=0.7\linewidth]{refined_overlayed_corners.png}};
			\begin{scope}[x={(image.south east)},y={(image.north west)}]
				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
				\spy[blue] on (3.5,3.0) in node [right] at (6.1,3.3);
			\end{scope}
		\end{tikzpicture}
		\caption{Additional features detection on the board with partial board occlusion
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{figure}

@@

	\begin{figure}
		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=4cm, connect spies}]
			\node[anchor=south west,inner sep=0] (image) at (0,0)
			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
			{\includegraphics[width=0.6\linewidth]{refined_corners1.png}};
			\begin{scope}[x={(image.south east)},y={(image.north west)}]
				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
				\spy[blue] on (4.8,2.5) in node [right] at (6.1,3.3);
			\end{scope}
		\end{tikzpicture}
		\caption{Newly detected points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{figure}

@@

\begin{frame}
	\frametitle{Evaluation (real data) 2}

	\begin{figure}
		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=5cm, connect spies}]
			\node[anchor=south west,inner sep=0] (image) at (0,0)
			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
			{\includegraphics[width=0.75\linewidth]{refined_corners2.png}};
			\begin{scope}[x={(image.south east)},y={(image.north west)}]
				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
				\spy[blue] on (3.0,2.4) in node [right] at (6.1,3.3);
			\end{scope}
		\end{tikzpicture}
		\caption{Newly detected points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Evaluation (real data, false positives)}

	\begin{figure}
		\begin{tikzpicture}[spy using outlines={circle,yellow,magnification=4,size=5cm, connect spies}]
			\node[anchor=south west,inner sep=0] (image) at (0,0)
			% {\includegraphics[width=0.6\textwidth]{distorted_image}};
			{\includegraphics[width=0.7\linewidth]{refined_corners_bad_bad.png}};
			\begin{scope}[x={(image.south east)},y={(image.north west)}]
				% \spy[red] on (2.5,1.4) in node [left] at (10.1,1.7);
				\spy[blue] on (2.6,2.0) in node [right] at (6.1,3.3);
			\end{scope}
		\end{tikzpicture}
		\caption{Example of false positives
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{figure}

@@

\begin{frame}
	\frametitle{Comparison}
	\begingroup
	\scriptsize

	\setlength\tabcolsep{1.5pt} % default value: 6pt
	\begin{table}
		\begin{tabularx}{\textwidth}{@{} L *{6}{c} @{}}
			\toprule
			\multicolumn{1}{c}{\multirow{2}{*}{\centering\textbf{Supports}}}           &
			\multicolumn{6}{c@{}}{\textbf{Name}}                                                                  \\
			\cmidrule(l){2-7}                                                          &
			\textbf{OpenCV\footcite{dudaAccurateDetectionLocalization2018}}            &
			\textbf{TartanKalib\footcite{duisterhofTartanCalibIterativeWideAngle2022}} &
			\textbf{Kalibr\footcite{mayeSelfsupervisedCalibrationRobotic2013}}         &
			\textbf{OCamCalib\footcite{scaramuzzaToolboxEasilyCalibrating2006}}        &
			\textbf{LIBCBDETECT\footcite{geigerAutomaticCameraRange2012}}              &
			{\normalsize \textbf{Ours}}                                                                           \\
			\midrule
			Unknown board shape                                                        & \xmark & \cmark & \cmark
			                                                                           & \cmark & \cmark & \cmark \\
			\hline
			Occlusion                                                                  & \xmark & \cmark & \cmark
			                                                                           & \cmark & \cmark & \cmark \\
			\hline
			Model-based extra features detection                                       & \xmark & \cmark & \xmark
			                                                                           & \xmark & \xmark & \cmark \\
			\hline
			Geometry-based extra features detection                                    & \xmark & \xmark & \xmark
			                                                                           & \xmark & \xmark & \cmark \\
			\bottomrule
		\end{tabularx}
		\caption{Comparison of feature detectors}
	\end{table}
	\endgroup
\end{frame}

@@

\begin{frame}
	\frametitle{Answers to the research questions}

	\begin{itemize}
		\item \textbf{How to find additional features on the calibration board which were not
			      detected by the feature detector?}\\

		      This thesis proposes a model-based approach to improve the detection of
		      calibration board fiducials from calibration imagery taken by wide-angle or
		      fisheye lenses.
		\item \textbf{How to filter out falsely detected features?}\\

		      We proposed a classifier that filters false positives, and
		      shown that it works well on real data.
		\item \textbf{Is there a need for finding additional features on the calibration
			      board? Are all of the points detected?}\\

		      We demonstrated that the proposed method successfully detected
		      additional features on the real data.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Reviewers' comments 1}
	\textbf{No comparison was made to classical camera calibration results}

	The main contribution is the feature detection step.

	The algorithm estimates camera parameters, but we don't claim that they are
	better than state-of-the-art. The user can use those, or pass the refined
	features into any camera calibration toolchain.
	% The user can use the
	% obtained camera parameters, however, we do not claim that they will always beat the
	% SOTA. Alternatively, the user should pass the refined features to any camera
	% calibration toolchain.
\end{frame}

\begin{frame}
	\frametitle{Reviewers' comments 2}
	\textbf{The literature review
		does not include a review of methods that solve the feature detection step in
		a different way}

	A review of feature detection methods is presented in the paper.

	The specific subtask of model-based missed
	feature detection is not big enough to have a separate review. However, we
	included TartanKalib\footcite{duisterhofTartanCalibIterativeWideAngle2022}.
\end{frame}

\begin{frame}
	\frametitle{Reviewers' comments 3}
	\textbf{There is no general block diagram of the algorithm}

	\begin{figure}
		\begin{tikzpicture}[
				block/.style={rectangle, draw, align=center, minimum width=2cm, minimum
						height=1cm, font=\footnotesize},
				line/.style={draw, -latex}
			]
			\node [block] (block1) {Feature\\ detection};
			\node [block, right=of block1, minimum width=8cm, minimum height=3cm] (block2) {};
			\node [block, at={(block2.center)}, xshift=-2.0cm] (block3) {Initialize camera\\ parameters (\(R\), \(\mathbf{t}\), \(\boldsymbol{\lambda}\))\\ using the solver};
			\node [block, at={(block2.center)}, xshift=2.0cm] (block4) {Refine camera\\ parameters and\\ estimate \(K\)\\ by optimization};
			\node [block, below=of block4] (block5) {Impute the gaps in\\ the board, and\\ extend it};
			\node [block, left=of block5] (block6) {Get positions of\\ new points on\\ the image};
			\node [block, left=of block6] (block7) {Filter out\\ false positives};

			\node [above of=block2, node distance=1.8cm] {Camera calibration};

			\path [line] (block1) -- (block3);
			\path [line] (block3) -- (block4);
			% \path [line] (block2) -| (block3);
			% \path [line] (block2) -| (block4);
			% \path [line] (block3) -- (block5);
			\path [line] (block4) -- (block5);
			\path [line] (block5) -- (block6);
			\path [line] (block6) -- (block7);
		\end{tikzpicture}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Reviewers' comments 4}
	\textbf{It is not sufficiently described what results are obtained on
		test sets}

	The datasets we used did not contain the ground truth camera calibration.
	Also, the algorithm does not include the learning step, hence there is no
	reason to use the test set.
	% Also, we used three datasets with different setup.
\end{frame}

\begin{frame}
	\frametitle{Reviewers' comments 4}
	\textbf{The questions "How to filter incorrectly defined grid points" and "Is there a
		need to search for additional grid points" posed in the work are insufficiently disclosed}

	Addressed in section Conclusions.
\end{frame}

\begin{frame}
	\frametitle{Reviewers' comments 5}
	\textbf{A comparison of the results with other feature detection methods has not been made}

	We have added a feature-wise comparison to the state-of-the-art methods, and
	numerical comparison to the
	LIBCBDETECT\footcite{geigerAutomaticCameraRange2012} method.

	The TartanKalib\footcite{duisterhofTartanCalibIterativeWideAngle2022} method
	currently supports only AprilGrid boards.
\end{frame}
